Analysis of NLA17 Dissolved Gas Indicator

### 2021-06-09 scripts/dgIndicatorAnalysis.Rmd
Minor tweaks to micromap code

## Linked micromaps
The ecoreg_stats summary is for population estimates.  The code at the bottom, ecoreg_pred, I believe gives summary stats for the predicted distributions, but I would double-check with Roy. There is a quick-and-dirty micromap code used to look trying linked micromap plots on different variables.  When you settle on the variables you want to use then the full micromap code produces the pretty linked micromap plots.
```{r, linked_micromap}

@@

ecoregions <- st_read("aggr_ecoregions_simple.shp")
wsa9names <- st_set_geometry(ecoregions, NULL) %>%
  select(WSA9, WSA9_NAME)

@@

# Full code:  Use this to produce final linked micromaps of the variables you want
# export as pdf US letter landscape from Plots pane
# export as PNG Width 900 Height 968, maintain aspect ratio
mmplot(stat.data=ecoreg_stats,
       map.data=ecor.polys,
       panel.types=c('dot_legend', 'labels', 'dot_cl', 'dot_cl', 'map'),
       panel.data=list(
         NA,
         'WSA9_NAME',
         list('post_med_n2o', 'LCI_n2o', 'UCI_n2o'),
         list('post_med_sat', 'LCI_sat', 'UCI_sat'),
         NA),
       ord.by = 'post_med_n2o', rev.ord = TRUE, grouping=3,
       median.row=FALSE,
       map.link=c('WSA9', 'ID'),

@@

>>>>

## Linked micromaps
The ecoreg_stats summary is for population estimates.  The code at the bottom, ecoreg_pred, I believe gives summary stats for the predicted distributions, but I would double-check with Roy. There is a quick-and-dirty micromap code used to look trying linked micromap plots on different variables.  When you settle on the variables you want to use then the full micromap code produces the pretty linked micromap plots.
```{r, linked_micromap}
# Read data object containing predictions for population
Sys.time()
load(paste0(localPath, "\\Environmental Protection Agency (EPA)\\ORD NLA17 Dissolved Gas - Documents\\inputData\\all_predictions.rda"))
Sys.time()

@@

ecoregions <- st_read(paste0(localPath, "\\Environmental Protection Agency (EPA)\\",
                             "ORD NLA17 Dissolved Gas - Documents\\inputData\\aggr_ecoregions_simple.shp"))

wsa9names <- st_set_geometry(ecoregions, NULL) %>%
  select(WSA9, WSA9_NAME)

@@

# Full code:  Use this to produce final linked micromaps of the variables you want
# export as pdf US letter landscape from Plots pane
# export as PNG Width 900 Height 968, maintain aspect ratio
tiff(filename = "output/figures/mmplot.tiff",
     res = 800, width = 9.00, height = 9.68, units = "in" )

mmplot(stat.data=ecoreg_stats,
       map.data=ecor.polys,
       panel.types=c('dot_legend', 'labels', 'dot_cl', 'dot_cl', 'map'),
       panel.data=list(
         NA,
         'WSA9_NAME',
         list('post_med_n2o', 'LCI_n2o', 'UCI_n2o'),
         list('post_med_sat', 'LCI_sat', 'UCI_sat'),
         NA),
       ord.by = 'post_med_n2o', rev.ord = TRUE, grouping=3,
       median.row=FALSE,
       map.link=c('WSA9', 'ID'),

@@

dev.off()
